Report on Late Winter2013 Production: Image Differencing

### 2013-03-29 W13report.tex

\subsection{Effect of Uncertainty on Measured ${S}\over{N}$}

@@

\subsection{Number of KernelCandidates}

@@

\subsection{Correlation with KernelCandidate Statistics}

@@

\section{Outstanding Issues}
We ran into several issues during this production that required work--arounds.  
In some cases we did not have the time to drill all the way down
to the root cause.  We itemize these issues here so that they may be addressed 
as part of the Summer 2013 work.

\subsection{Astrometric Registration \label{subsec-astrom}}
The original plan for this production was to use the single deep exposures (v6866600) as 
inputs to the coadd process, to exercise use of the coadd repository.  As 
such we warped the exposures to coadd patches for use in the image difference
task.  The register task was unable to solve a differential WCS between the coadd
and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
as it expands its polynomials around the CRPIX.  To get around this 
we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
scratch.  This worked fairly will part of the time,
yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
as we did not understand the origin of these problems, and there were legitimate bugs
in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
using the deep {\tt calexp} as the template directly; the direct {\tt calexp} to {\tt calexp} 
registration yielded residuals in the range of 5--7 mas (well, its 0.02 pixels).

>>>>

\subsection{Effect of Uncertainty on Measured ${S}\over{N}$ \label{sec-sn}}

@@

\subsection{Number of KernelCandidates {\bf ANDYB}}

@@

\subsection{Detection Threshold}
Obviously the number of false positives is strongly dependent on the detection threshold.  In order to
check the scaling of our false positive rates with detection threshold, we ran the same config (see \ref{tab-bestconfig10} 
for the config parameters)
at several detection threshold values for each visit both prefiltering and postfiltering.  As discussed in 
Section~\ref{sec-analyticfp} one can predict the number of false positives expected in a sensor given
seeing and threshold values.  Some example values of the number of false positives (both +ve and -ve)
expected in LSST size detectors are given in Table \ref{tab-fprate}.

As discussed in the Section \ref{sec-sn}, the accuracy of the noise estimation in the dection is crutial to 
understanding the false positive rate.  In the previous section we quantify the under--estimation of the variance
by the variance plane in the case of pre and post filtering.  In our analysis of the threshold dependence of
our false detection rate we must correct for this under--estimation in order to put the counts from each algorithm
on the same normalization.

Figure \ref{fig-fp_v_thresh} shows the results of this analysis.  In all figures red squares are postfiltered data and
blue circles are for the prefiltering technique.  All values are for the number of false positives in a 4000x4072 sensor.
Using a Monte Carlo approach we 
estimate the variance on the predicted false positive rate as a function of threshold.  The 1-$\sigma$ confidence envelope is shown
as shaded grey about the model line in dark black.  From left to right the panels are for visit 6866601 -- 0.6$^{\prime\prime}$ FWHM,
6866602 -- 0.88$^{\prime\prime}$ FWHM and 6866603 -- 1.2$^{\prime\prime}$ FWHM respectively.  Except in the case of deconovlution
in the postfiltering case (visit 6866601) the count rates between the two algorithms agree very well when corrected for the
observed under--estimation of the noise by the variance plane.  In the case where postfiltering requires a deconvolution, the high $\over{S}{N}$
detections come primarily from detection of the ringing around stars.

In all cases the empirical results are below the predicted results indicating
that the number counts are smaller than the theoretical floor.  {\bf What should we say about this here?} We can correct for this by scaling
the prediction by 2.5\%, 1.5\% and 1\% for visits 6866601, 6866602, and 6866603 respectively.  The data plotted with these corrections are shown
in the bottom row.  Once this correction is done, the trend of false positive rate with detection threshold agrees to within 1-$\sigma$ for the 
prefiltering case for all three seeing values.

\section{Results: Correlation with KernelCandidate Statistics {\bf ANDYB}}

@@

\section{Outstanding Issues}
We ran into some issues during this production that required work--arounds.  
In some cases we did not have the time to drill all the way down
to the root cause.  We itemize these issues here so that they may be addressed 
as part of the Summer 2013 work.

\subsection{Astrometric Registration \label{subsec-astrom}}
The original plan for this production was to use the single deep exposures (v6866600) as 
inputs to the coadd process, to exercise use of the coadd repository.  As 
such we warped the exposures to coadd patches for use in the image difference
task.  The register task was unable to solve a differential WCS between the coadd
and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
as it expands its polynomials around the CRPIX.  To get around this 
we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
scratch.  This worked fairly will part of the time,
yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
as we did not understand the origin of these problems, and there were legitimate bugs
in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
using the deep {\tt calexp} as the template directly; the direct deep {\tt calexp} to science {\tt calexp} 
registration typically yielded residuals in the range of 4--5 mas.
